Notes on Control Plane Inference

### 2021-05-25 inference.tex
finish sketching proof

\begin{definition}[Projections]
  For a set of variables $S \subseteq \Var$, and a packet $\pkt$, write
  $\pkt|_S$ to be projection of $\pkt$ onto $S$. \todo{I guess this means
    packets are partial functions?} Formally,
  \[\pkt|_S \triangleq \{x \mapsto \pkt(x) \mid x \in S\}.\]
  Two packets $\pkt$,
  $\pkt'$ are equivalent up to $S \subseteq \Var$, written $\pkt =_S \pkt'$, iff
  $\pkt|_S = \pkt'|_s$. A set of packets $P$ is a subset of $P'$ up to $S$,
  written $P \subseteq_S P'$ iff for every packet $\pkt \in P$, there exists
  $\pkt' \in P'$ such that $\pkt =_S \pkt'$. Two sets of packets $P$ and $P'$
  are equivalent up to $S$, written $P =_S P'$ iff $P \subseteq_S P'$ and $P \subseteq_S P'$.
\end{definition}

>>>>

\begin{definition}[Projections]
  For a set of variables $S \subseteq \Var$, and a packet $\pkt$, write
  $\pkt|_S$ to be projection of $\pkt$ onto $S$. \todo{I guess this means
    packets are partial functions?} Formally,
  \[\pkt|_S \triangleq \{x \mapsto \pkt(x) \mid x \in S\}.\]
  Two packets $\pkt$,
  $\pkt'$ are equivalent up to $S \subseteq \Var$, written $\pkt =_S \pkt'$, iff
  $\pkt|_S = \pkt'|_s$. A set of packets $P$ is a subset of $P'$ up to $S$,
  written $P \subseteq_S P'$ iff for every packet $\pkt \in P$, there exists
  $\pkt' \in P'$ such that $\pkt =_S \pkt'$. Two sets of packets $P$ and $P'$
  are $S$-equivalent, written $P =_S P'$ iff $P \subseteq_S P'$ and $P \subseteq_S P'$.
\end{definition}

\begin{lemma}[Projection]
  For $c \in \Cmd$, $\fvs(c) \subseteq V \subseteq \Var$ and $P \subseteq \Pkt$ such that $\forall
  \pkt_1,\pkt_2 \in P, \pkt_1 =_V \pkt_2$, $\denote{c} P =_V \denote{c} P|_V$.

\end{lemma}
